%! Author = adrienkoumgangtegantchouang
%! Date = 07/06/25


\chapter*{Acknowledgments}\label{ch:acknowledgments}



First and foremost, I would like to express my deepest gratitude to \textbf{God}, whose grace, strength, and guidance sustained me throughout the duration of this project.

I sincerely thank all the \textbf{professors and academic staff} who provided the foundation, mentorship, and encouragement that made this work possible.
Your knowledge and dedication have been invaluable.

I would also like to acknowledge the \textbf{authors of NoSQL for Mere Mortals} for their clear explanations and practical approach, which greatly enhanced my understanding of NoSQL data modeling.

My heartfelt thanks to the developers and contributors of the various \textbf{tools and frameworks} used in this project
— including \textbf{Flask}, \textbf{React}, \textbf{MongoDB}, \textbf{Redis}, and \textbf{Docker}
— as well as the extensive and well-maintained \textbf{documentation} that enabled effective development.

Special thanks to \textbf{DeepL}, which helped with accurate and nuanced \textbf{translations},
and to \textbf{ChatGPT} and \textbf{DeepSeek}, whose assistance in technical guidance, code generation,
and documentation structuring significantly accelerated the progress and quality of this work.

I extend my heartfelt thanks to my friends for their moral support, encouragement, and constant motivation.
Their presence has been a great source of strength.

Finally, I thank my girlfriend for her patience, love, and unwavering support throughout this journey.

Finally, I am grateful to all those who supported me, directly or indirectly, in the successful completion of this project.




